
## <br>Newmark Displacements

```{r}
IDn_TARGET <- "ensemble"
IDg_TARGET <- IDg_gmdp
Da_TARGET  <- Da_gmdp
p_TARGET   <- c("mean", 0.84)
CAP <- "Newmark sliding-block model. Residual displacements [cm] for model %s. All geometrical scenarios shown. Values are reported for target ground motion with 1/%.0f AEP [1/yr]."
TR_LABEL <- prettyNum(TR_gmdp, big.mark = ",", scientific = FALSE)
```

:::{.panel-tabset }

### $D_n$ (`r ID_gmdp[1]`)

```{r}
ID_TARGET <- paste0(ID_gmdp[1], ".max")
```

:::{.panel-tabset .full-width }

#### $T_R\approx `r TR_LABEL[2]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[2]
```
{{< include /_fig/Dn_IDn.qmd >}}

#### $`r TR_LABEL[3]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[3]
```
{{< include /_fig/Dn_IDn.qmd >}}

#### $`r TR_LABEL[4]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[4]
```
{{< include /_fig/Dn_IDn.qmd >}}

#### $`r TR_LABEL[5]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[5]
```
{{< include /_fig/Dn_IDn.qmd >}}

#### $`r TR_LABEL[6]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[6]
```
{{< include /_fig/Dn_IDn.qmd >}}

#### $`r TR_LABEL[7]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[7]
```
{{< include /_fig/Dn_IDn.qmd >}}

#### $`r TR_LABEL[8]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[8]
```
{{< include /_fig/Dn_IDn.qmd >}}

:::

### $D_n$ (`r ID_gmdp[2]`)

```{r}
ID_TARGET <- paste0(ID_gmdp[2], ".max")
```

:::{.panel-tabset .full-width }

#### $T_R\approx `r TR_LABEL[2]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[2]
```
{{< include /_fig/Dn_IDn.qmd >}}

#### $`r TR_LABEL[3]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[3]
```
{{< include /_fig/Dn_IDn.qmd >}}

#### $`r TR_LABEL[4]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[4]
```
{{< include /_fig/Dn_IDn.qmd >}}

#### $`r TR_LABEL[5]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[5]
```
{{< include /_fig/Dn_IDn.qmd >}}

#### $`r TR_LABEL[6]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[6]
```
{{< include /_fig/Dn_IDn.qmd >}}

#### $`r TR_LABEL[7]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[7]
```
{{< include /_fig/Dn_IDn.qmd >}}

#### $`r TR_LABEL[8]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[8]
```
{{< include /_fig/Dn_IDn.qmd >}}

:::

:::

```{r}
#| include: false
rm(ID_TARGET, IDn_TARGET, IDg_TARGET, Da_TARGET, p_TARGET, TR_TARGET, TR_LABEL, CAP)
```

## <br>Newmark Displacements

```{r}
IDn_TARGET <- c(IDn_gmdp, "ensemble")
Da_TARGET  <- Da_gmdp
p_TARGET   <- c("mean", 0.84)
CAP <- "Newmark sliding-block model. Residual displacements [cm] for geometry %s (scenario %d). All Newmark models shown. Values are reported for target ground motion with 1/%.0f AEP [1/yr]."
TR_LABEL <- prettyNum(TR_gmdp, big.mark = ",", scientific = FALSE)
```

:::{.panel-tabset }

### $D_n$ (`r ID_gmdp[1]`)

```{r}
ID_TARGET <- paste0(ID_gmdp[1], ".max")
```

:::{.panel-tabset .full-width }

#### $T_R\approx `r TR_LABEL[2]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[2]
```
{{< include /_fig/Dn_IDg.qmd >}}

#### $`r TR_LABEL[3]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[3]
```
{{< include /_fig/Dn_IDg.qmd >}}

#### $`r TR_LABEL[4]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[4]
```
{{< include /_fig/Dn_IDg.qmd >}}

#### $`r TR_LABEL[5]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[5]
```
{{< include /_fig/Dn_IDg.qmd >}}

#### $`r TR_LABEL[6]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[6]
```
{{< include /_fig/Dn_IDg.qmd >}}

#### $`r TR_LABEL[7]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[7]
```
{{< include /_fig/Dn_IDg.qmd >}}

#### $`r TR_LABEL[8]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[8]
```
{{< include /_fig/Dn_IDg.qmd >}}

:::

### $D_n$ (`r ID_gmdp[2]`)

```{r}
ID_TARGET <- paste0(ID_gmdp[2], ".max")
```

:::{.panel-tabset .full-width }

#### $T_R\approx `r TR_LABEL[2]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[2]
```
{{< include /_fig/Dn_IDg.qmd >}}

#### $`r TR_LABEL[3]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[3]
```
{{< include /_fig/Dn_IDg.qmd >}}

#### $`r TR_LABEL[4]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[4]
```
{{< include /_fig/Dn_IDg.qmd >}}

#### $`r TR_LABEL[5]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[5]
```
{{< include /_fig/Dn_IDg.qmd >}}

#### $`r TR_LABEL[6]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[6]
```
{{< include /_fig/Dn_IDg.qmd >}}

#### $`r TR_LABEL[7]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[7]
```
{{< include /_fig/Dn_IDg.qmd >}}

#### $`r TR_LABEL[8]`\,yr$
```{r}
TR_TARGET <- TR_gmdp[8]
```
{{< include /_fig/Dn_IDg.qmd >}}

:::

:::

```{r}
#| include: false
rm(ID_TARGET, IDn_TARGET, Da_TARGET, p_TARGET, TR_TARGET, TR_LABEL, CAP)
```
