##  Regional Sources (SSM)

The seismic source model (SSM) defines the spatial distribution, geometry, and earthquake occurrence rates of all seismogenic sources considered capable of contributing to ground-motion hazard at a site. In the hazard integral ([@eq-hazard-integral]), the SSM provides the magnitude-frequency distributions $f_{M,s}(m)$, the spatial distributions $f_{\mathbf{R}|M,s}(\mathbf{r}|m)$, the occurrence rates $\nu_0^{(s)}$, and the maximum magnitude $M_{\max}^{(s)}$ for each source $s$ [@Cornell1968; @SSHAC1997]. Epistemic uncertainty in these parameters is captured through the source-model logic tree described in [@sec-ssm].

This appendix documents the Indian Subcontinent SSM adopted in this assessment, including the source inventory, logic-tree structure, recurrence parameters, magnitude-frequency distribution types, magnitude-area scaling relationships, maximum magnitude characterization, and seismogenic depth architecture. The model is implemented in the OpenQuake Engine through source-model XML files referenced by the logic tree.

### Source Inventory

The IND model is based on the probabilistic seismic hazard model for the Indian subcontinent developed by Nath and Thingbaijam [@NathThingbaijam2012], subsequently updated and translated into OpenQuake format in collaboration with Natural Resources Canada (version v2012.2.0), as documented in the GEM model report [@GemInd2012]. The model domain extends from approximately $60.0^\circ$E to $100.8^\circ$E in longitude and $2.0^\circ$N to $40.0^\circ$N in latitude, covering India, Bangladesh, Bhutan, Nepal, Pakistan, Myanmar, and surrounding regions of the Indian subcontinent. The minimum earthquake magnitude ($M_{\min}$) adopted for hazard calculations is 4.5 Mw across all area sources; the two smoothed-seismicity grids employ $M_{\min}$ thresholds of 4.5 Mw and 5.5 Mw respectively.

The IND SSM comprises 443,197 seismic sources of two types: 108 area sources (`areaSource`) and 443,089 point sources (`pointSource`). These sources span four tectonic region types (TRTs); the table below provides the complete census by TRT and source type.

```{r}
#| include: true
#| label: tbl-ssm-ind-inventory
#| tbl-cap: "Source inventory by tectonic region type."

DT <- data.table::data.table(
  `Description` = c("Subduction Intraslab", "Subduction Interface", "Stable Continental Crust", "Active Shallow Crust", "Total"),
  `TRT` = c("SIS", "SIF", "SCC", "ASC", ""),
  `Area sources` = c("35", "27", "17", "29", "108"),
  `Point sources` = c("139,942", "123,748", "94,433", "84,966", "443,089"),
  `Total` = c("139,977", "123,775", "94,450", "84,995", "443,197")
)

TBL <- DT |> buildTable(
  library = "flextable",
  align.body = "center",
  font.size.body = FONT.SIZE.BODY,
  font.size.header = FONT.SIZE.HEADER
) |>
  flextable::set_table_properties(layout = "autofit")
TBL
```

The SSM is defined through logic-tree XML files. The primary logic tree references three source-model XML files and produces 27 end-branches from the Cartesian product of three branch sets ($3 \times 3 \times 3 = 27$). The branch set structure is described in detail in the Logic Tree Structure section below.

Seismic-source characterisation follows the classical PSHA framework outlined by Cornell [@Cornell1968] and formalised under SSHAC guidelines [@SSHAC1997]. Sources are delineated from geologic, geophysical, and seismological evidence, with geometry and parametrisation defined in OpenQuake source-model XML files. The implementation is publicly available at the `nackerley/indian-subcontinent-psha` repository on GitHub [@NackerleyRepo].

### Logic Tree Structure

The source-model logic tree encodes epistemic uncertainty through three branch sets, collectively producing $3 \times 3 \times 3 = 27$ end-branches. Each branch set addresses a distinct type of epistemic uncertainty; branches within each set carry weights reflecting the relative credibility of each alternative [@GemInd2012].

Branch set 1 addresses source-model selection, offering three alternative source-model representations of the regional seismicity. Branch `b1m1` selects the 108-zone areal source model; branches `b1m2` and `b1m3` select spatially smoothed point-source grids with $M_{\min}$ thresholds of 4.5 Mw and 5.5 Mw respectively.

```{r}
#| include: true
#| label: tbl-ssm-ind-bs1
#| tbl-cap: "Branch set 1: source-model selection."

DT <- data.table::data.table(
  `Branch` = c("b1m1", "b1m2", "b1m3"),
  `Model file` = c("nt2012_areal_source_model_v1.xml", "nt2012_smoothed_source_model_v1_mmin4.5.xml", "nt2012_smoothed_source_model_v1_mmin5.5.xml"),
  `Weight` = c("0.40", "0.27", "0.33")
)

TBL <- DT |> buildTable(
  library = "flextable",
  align.body = "center",
  font.size.body = FONT.SIZE.BODY,
  font.size.header = FONT.SIZE.HEADER
) |>
  flextable::set_table_properties(layout = "autofit")
TBL
```

Branch set 2 applies simultaneous relative perturbations to the base $M_{\max}$ of all sources. The symmetric flanking branches ($\pm 0.3$ Mw) each carry weight 0.32; the unperturbed central branch carries the higher weight of 0.36, reflecting greater credibility attributed to the nominal parameter estimate.

```{r}
#| include: true
#| label: tbl-ssm-ind-bs2
#| tbl-cap: "Branch set 2: maximum magnitude perturbation."

DT <- data.table::data.table(
  `Branch` = c("b2m1", "b2m2", "b2m3"),
  `Perturbation (Mw)` = c("-0.3", "0.0", "+0.3"),
  `Weight` = c("0.32", "0.36", "0.32")
)

TBL <- DT |> buildTable(
  library = "flextable",
  align.body = "center",
  font.size.body = FONT.SIZE.BODY,
  font.size.header = FONT.SIZE.HEADER
) |>
  flextable::set_table_properties(layout = "autofit")
TBL
```

Branch set 3 applies simultaneous relative perturbations to the Gutenberg-Richter $b$-value of all sources, with the same symmetric weight structure as branch set 2.

```{r}
#| include: true
#| label: tbl-ssm-ind-bs3
#| tbl-cap: "Branch set 3: b-value perturbation."

DT <- data.table::data.table(
  `Branch` = c("b3m1", "b3m2", "b3m3"),
  `Perturbation` = c("-0.1", "0.0", "+0.1"),
  `Weight` = c("0.32", "0.36", "0.32")
)

TBL <- DT |> buildTable(
  library = "flextable",
  align.body = "center",
  font.size.body = FONT.SIZE.BODY,
  font.size.header = FONT.SIZE.HEADER
) |>
  flextable::set_table_properties(layout = "autofit")
TBL
```

The combined weights within each branch set sum to unity: source-model branches sum to $0.40 + 0.27 + 0.33 = 1.00$; both perturbation branch sets sum to $0.32 + 0.36 + 0.32 = 1.00$.

### Earthquake Recurrence Parameters

All 108 area sources employ the truncated Gutenberg-Richter MFD (`truncGutenbergRichterMFD`), parameterised by an $a$-value and a $b$-value with explicit $M_{\min}$ and $M_{\max}$ bounds. The minimum magnitude is 4.5 Mw for area sources in Active Shallow Crust, Stable Continental Crust, and Subduction Interface settings; Subduction Intraslab sources encompass a range of $M_{\min}$ values from 4.5 to 7.5 Mw reflecting the variable depth of deep slab zones. Epistemic uncertainty in the $b$-value is captured through logic-tree branch set 3, which applies simultaneous relative perturbations of $-0.1$, $0.0$, and $+0.1$ (weights 0.32, 0.36, 0.32); $M_{\max}$ uncertainty treatment is addressed in the Maximum Magnitude section below. The two smoothed-seismicity point-source grids inherit the same Gutenberg-Richter parametrisation from the parent areal zones, distributed over a regular spatial grid; individual grid nodes carry spatially redistributed $a$-values derived from parent zone rates rather than independently fitted catalogue statistics [@NathThingbaijam2012].

@tbl-ssm-ind-recurrence summarises the recurrence parameters for the 108 area sources grouped by tectonic region type. The $M_{\max}$ values are base (central) estimates prior to application of the $M_{\max}$ logic-tree perturbation.

```{r}
#| include: true
#| label: tbl-ssm-ind-recurrence
#| tbl-cap: "Earthquake recurrence parameters by tectonic region type (108 area sources, base values)."

DT <- data.table::data.table(
  `Tectonic region` = c("Active Shallow Crust (ASC)", "Stable Continental Crust (SCC)", "Subduction Interface (SIF)", "Subduction Intraslab (SIS)"),
  `MFD type` = c("truncGR", "truncGR", "truncGR", "truncGR"),
  `a-value range` = c("2.73-7.08", "1.58-4.84", "3.12-5.40", "3.22-7.33"),
  `b-value range` = c("0.72-1.37", "0.63-1.19", "0.72-1.24", "0.80-1.57"),
  `Mmin (Mw)` = c("4.5", "4.5", "4.5", "4.5-7.5"),
  `Mmax range (Mw)` = c("7.0-8.8", "6.0-8.2", "6.5-9.4", "6.5-8.6"),
  `n` = c("29", "17", "27", "35")
)

TBL <- DT |> buildTable(
  library = "flextable",
  align.body = "center",
  font.size.body = FONT.SIZE.BODY,
  font.size.header = FONT.SIZE.HEADER
) |>
  flextable::set_table_properties(layout = "autofit")
TBL
```

### Magnitude-Frequency Distribution Types

The IND source model employs a single MFD type for all 108 area sources and all smoothed-seismicity point-source grids: the truncated Gutenberg-Richter distribution (`truncGutenbergRichterMFD`). Under this parametrisation, earthquake occurrence rates are expressed as a log-linear function of magnitude, bounded at $M_{\min}$ and $M_{\max}$, and governed by the $a$-value (total activity rate intercept at the reference magnitude) and the $b$-value (slope of the frequency-magnitude relation). The `incrementalMFD`, `arbitraryMFD`, and `multiMFD` distribution types are not present in this model; characteristic or hybrid MFD formulations are likewise absent.

### Magnitude-Area Scaling Relationships

Three magnitude-area scaling relationships are applied across different tectonic environments to relate moment magnitude to rupture dimensions. The Wells and Coppersmith (1994) relationship (`WC1994`) [@WellsCoppersmith1994] is applied to 46 area sources in Active Shallow Crust and Stable Continental Crust settings. The Strasser et al. (2010) intraslab relationship (`StrasserIntraslab`) [@Strasser2010] is applied to 35 area sources in Subduction Intraslab settings. The Strasser et al. (2010) interface relationship (`StrasserInterface`) [@Strasser2010] is applied to 27 area sources in Subduction Interface settings. The sum $46 + 35 + 27 = 108$ accounts for all area sources. All area sources adopt a rupture aspect ratio of 2.0.

### Slip-Rate Data and Moment Balance

Activity rates for fault sources with available slip-rate data are in principle derived from seismic-moment balance, where the seismic moment rate $\dot{M}_0$ is related to the shear modulus $\mu$, fault area $A$, and long-term slip rate $S$:

$$\dot{M}_0 = \mu\, A\, S$$

The IND source model contains no fault sources. The complete source inventory consists exclusively of 108 areal seismogenic zones and 443,089 spatially distributed point sources in two smoothed-seismicity grids; no fault-source XML files are present, and no slip-rate data are specified for any source. Accordingly, the number of sources with slip-rate data is zero, and no slip-rate range is applicable within this model. Recurrence parameters for all area sources are derived from seismological catalogue statistics via Gutenberg-Richter fitting, as documented in the source-model implementation [@NathThingbaijam2012][@GemInd2012].

### Maximum Magnitude

Maximum magnitude ($M_{\max}$) defines the upper bound of the MFD for each source and is a critical parameter controlling the tail of the hazard curve. For all 108 area sources, base $M_{\max}$ values range from 6.0 to 9.4 Mw across the four tectonic region types, reflecting environments spanning from stable continental crust to subduction megathrust settings. The highest base $M_{\max}$ values correspond to Subduction Interface zones -- such as the Sumatra and Himalaya-Main Frontal Thrust systems -- where great earthquakes exceeding $M$ 8.5 are considered possible. $M_{\max}$ values are assigned per zone from the seismotectonic characterisation study by Nath and Thingbaijam [@NathThingbaijam2012] and are set as explicit parameters within the `truncGutenbergRichterMFD` specification.

Epistemic uncertainty in $M_{\max}$ is captured through `maxMagGRRelative` logic-tree branch set 2, which applies simultaneous perturbations of $\Delta = -0.3$, $0.0$, and $+0.3$ Mw to all sources (weights 0.32, 0.36, 0.32). For the smoothed-seismicity point-source grids, $M_{\max}$ is inherited from the parent areal zone parametrisation; point-source $M_{\max}$ values are not independently constrained and follow the same global perturbation scheme.

@tbl-ssm-ind-mmax summarises the base $M_{\max}$ ranges by tectonic region type together with the derived epistemic bounds.

```{r}
#| include: true
#| label: tbl-ssm-ind-mmax
#| tbl-cap: "Maximum magnitude characterisation by tectonic region type (base and epistemic bounds, area sources)."

DT <- data.table::data.table(
  `Tectonic region` = c("ASC", "SCC", "SIF", "SIS"),
  `Base Mmax (Mw)` = c("7.0-8.8", "6.0-8.2", "6.5-9.4", "6.5-8.6"),
  `Low (delta -0.3, Mw)` = c("6.7-8.5", "5.7-7.9", "6.2-9.1", "6.2-8.3"),
  `High (delta +0.3, Mw)` = c("7.3-9.1", "6.3-8.5", "6.8-9.7", "6.8-8.9"),
  `Derivation method` = c("truncGutenbergRichterMFD", "truncGutenbergRichterMFD", "truncGutenbergRichterMFD", "truncGutenbergRichterMFD")
)

TBL <- DT |> buildTable(
  library = "flextable",
  align.body = "center",
  font.size.body = FONT.SIZE.BODY,
  font.size.header = FONT.SIZE.HEADER
) |>
  flextable::set_table_properties(layout = "autofit")
TBL
```

### Seismogenic Depth Parameters

The seismogenic depth model in the IND SSM reflects a multi-layer structure consistent with the tectonic environment assigned to each source zone. Active Shallow Crust (ASC) sources are confined to the upper 25 km, with upper seismogenic depth $z_{\text{upper}}$ = 0 km, lower seismogenic depth $z_{\text{lower}}$ = 25 km, and mean hypocentral depth 15 km. Stable Continental Crust (SCC) sources span $z_{\text{upper}}$ = 0-25 km and $z_{\text{lower}}$ = 25-70 km, with mean hypocentral depths of 15-25 km. Subduction Interface (SIF) sources exhibit $z_{\text{upper}}$ = 0-70 km and $z_{\text{lower}}$ = 25-180 km, with mean hypocentral depths of 15-70 km. Subduction Intraslab (SIS) sources occupy the deepest zone, with $z_{\text{upper}}$ = 25-180 km, $z_{\text{lower}}$ = 70-300 km, and mean hypocentral depths of 25-180 km. Hypocentral depth distributions are specified as single-value distributions with probability 1.0 for all area sources; that is, a single representative hypocentral depth is assigned deterministically to each zone.

```{r}
#| include: true
#| label: tbl-ssm-ind-depth
#| tbl-cap: "Seismogenic depth parameters by tectonic region type (area sources)."

DT <- data.table::data.table(
  `Tectonic region` = c("Active Shallow Crust (ASC)", "Stable Continental Crust (SCC)", "Subduction Interface (SIF)", "Subduction Intraslab (SIS)"),
  `z_upper (km)` = c("0", "0-25", "0-70", "25-180"),
  `z_lower (km)` = c("25", "25-70", "25-180", "70-300"),
  `Mean hypocentral depth (km)` = c("15", "15-25", "15-70", "25-180")
)

TBL <- DT |> buildTable(
  library = "flextable",
  align.body = "center",
  font.size.body = FONT.SIZE.BODY,
  font.size.header = FONT.SIZE.HEADER
) |>
  flextable::set_table_properties(layout = "autofit")
TBL
```

The depth structure reflects a three-layer architecture: shallow crustal sources (ASC and the upper SCC layer) are confined to the uppermost 25 km; intermediate-depth zones (lower SCC and the upper portions of the subduction envelopes) extend to 70 km; and deep subduction intraslab zones reach 300 km depth. The wide depth ranges for SIF and SIS reflect the global variability of subduction geometries included in the model domain, from shallow interface contact zones to deep slab ruptures.
